DIAGNOSTIC SUPPORT OF SKIN LESION CLASSIFICATION USING CNN AND SOFT ATTENTION

### 2022-08-20 MDPI/Sensor Paper/template.tex
Update

\address{
$^{1}$ \quad Faculty: Information Technology, University of Transport and Communications, Vietnam \\
$^{2}$ \quad Faculty: Information Technology, University of Transport and Communications, Vietnam\\
$^{3}$ \quad Faculty: Information Technology, University of Transport and Communications, Vietnam}

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Today, the rapid development of industrial zones leads to an increased incidence of skin	diseases because of polluted air. According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffering from skin cancer and more than 7600 of these people will not survive. In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential. Along with the strong development of artificial intelligence technologies, many solutions and tools to support the diagnosis of skin diseases have been researched and developed. These include DenseNet, InceptionNet, ResNet, NasNet, SeNet, EfficientNet, VGGNet. In this study, another approach to building tools to aid in the diagnosis of skin pathologies is proposed. SOTA (state of the art) models DenseNet, InceptionNet, ResNet, NasNet, MobileNet combined with Soft-Attention are used as backbone. In addition, personal information such as age and gender are also used. In addition, a new loss function	that takes into account the imbalance of the data is also proposed. Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.989, respectively, are improvements compared to published indexes. Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of floors is 4 times less, it achieves 86 percent accuracy and 30 times faster diagnosis.}

@@

\begin{table}
	\centering
	\begin{tabular}{| c | p{1.5cm} | p{1.5cm} | p{2cm} | p{1.5cm} | p{2cm} |}
		\hline
		Research & Deep Learning & Machine Learning & Data 
		Augmentation & Feture Extraction & Data set\\
		\hline
		\cite{03358} & x & & x & & HAM10000\\
		\hline
		\cite{03798} & x & x & x & x & HAM10000\\
		\hline
		\cite{10348} & x & x & x & & HAM10000, $PH^2$\\
		\hline
		\cite{09418} & x & & x & & HAM10000\\
		\hline
		\cite{01284} & x & & x & & HAM10000\\
		\hline
		\cite{06612} & x & & x & x & HAM10000, BCN-20000, MSK\\
		\hline
		\cite{03225} & x & & x & & HAM10000\\
		\hline
		\cite{12602} & x & & x & & HAM10000\\
		\hline
		\cite{03426} & x & & x & & HAM10000\\
		\hline
		\cite{03910} & x & & x & & HAM10000\\
		\hline
		\cite{05045} & & x & x & x & HAM10000\\
		\hline
	\end{tabular}
	\caption{Related Works Summary. This table is a summary of the approach to skin lesion classification and segmentation. The first column illustrate the cite to the paper research. Column 2 shows a brief summary of the method that is stated in the associated paper.}
	\label{table:related-work-summary}
\end{table}
\subsection{Proposed Method}
In this research, a new model is constructed from the combination of:\\
- Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and MobileNetV2/V3\\
- Using metadata including age, gender, localization as another input of the model\\
- Using Soft-Attention as a feature extractor of the model\\
- A new weight loss function
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
\subsection{Materials}
\subsubsection{Image Data}
The data set used in this paper is the HAM10000 data set published by Havard University Dataverse \cite{10417}. There are total 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the data set is shown in the table \ref{table:data-distribution} below:

\begin{table}[H]
	\centering
	\begin{tabular}{|c c c c c c c c c|} 
		\hline
		Class & AKIEC & BCC & BKL & DF & MEL & NV & VASC & Total \\ 
		\hline
		No. Sample & 327 & 514 & 1099 & 115 & 1113 & 6705 & 142 & 10015 \\
		\hline
	\end{tabular}
	\caption{Data Distribution in HAM10000. This table illustrate the distribution of all class in the data set. The detail name of the skin disease in the data set can be found at the Abbreviations}
	\label{table:data-distribution}
\end{table}

@@

\subsubsection{Metadata}
The HAM10000 data set \cite{10417} also contain the metadata of patient including gender, age, and the capturing position illustrated in table \ref{table:metadata sample}
\begin{table}[H]
	\centering
	\begin{tabular}{|c c c c |} 
		\hline
		ID & Age & Gender & Local\\ 
		\hline
		ISIC-00001 & 15 & Male & back\\
		\hline
		ISIC-00002 & 85 & Female & elbow\\
		\hline
	\end{tabular}
	\caption{Metadata example in the data set}
	\label{table:metadata sample}
\end{table}
\subsection{Methodology}
\subsubsection{Overall Architecture}
The whole architecture of the model is represented in the figure \ref{fig:main-model}. The model takes two input including Image data and Metadata. Metadata branch, otherwise is preprocessed before feeding into a dense layer then concatenate with the output of Soft-Attention layer.

@@

The figure \ref{fig:model-structure} illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research. In detailed the combination of DenseNet201 and Soft-Attention is formed by replacing the three last DenseBlock, Global Average Pooling, and the fully-connected layer with the Soft-Attention Module. Similarity, ResNet50 and ResNet152 is also replaced the three last Residual Block, Global Average Pooling, and the fully connected layer with the Soft-Attention module. InceptionResNetV2, on the other hand, is replaced the Average Pool and the last Dropout with the Soft-Attention Module. Besides, the two last Normal Cell in NasNetLarge is replaced with the Soft-Attention module.

@@

The figure \ref{fig:mobile-model-structure}, on the other hand shows the detailed structure of mobile-based mobile and its combination with Soft-Attention. All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution 1x1 by Soft-Attention module. The NasNetMobile, otherwise, combine with the Soft-Attention module by replacing the last Normal Cell. 
\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/Mobile Model Structure}
	\caption{Overall Mobile-based Model Architecture. This figure show the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile. The detail structure and information can be found at the Apendix \ref{appendix-table:detailed mobile model structure}}
	\label{fig:mobile-model-structure}
\end{figure}

@@

In this paper, the unknowns is kept as a type as discussed in Metadata section. Sex, anatomical site and age are also category encoded and numerical normalized, respectively. After processing, the metadata is then concatenated and fed into a dense layer of 4096 neurons. Finally, this this dense layer is then concatenate with the output of Soft-Attention which is then discussed in Soft-Attention section. The Input schema is described in the table \ref{fig:input-schema}

@@

\begin{table}[H]
	\centering
	\begin{tabular}{|l | c c c|} 
		\hline
		Model & Size(MB) & Parameters & Depth \\ 
		\hline
		Resnet50 & 98 & 25.6M & 107 \\ 
		\hline
		Resnet152 & 232 & 60.4M & 311 \\ 
		\hline
		DenseNet201 & 80 & 20.2M & 402 \\
		\hline
		InceptionResNetV2 & 215 & 55.9M & 449 \\
		\hline
		MobileNet & 16 & 4.3M & 55 \\ 
		\hline
		MobileNetV2 & 14 & 3.5M & 105 \\ 
		\hline
		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
		\hline
		MobileNetV3Large & Unknown & 5.5M & 118 \\
		\hline
		NasnetMobile & 23 & 5.3M & 308 \\
		\hline
		NasnetLarge & 343 & 88.9M & 533 \\ 
		\hline
	\end{tabular}
	\caption{Size and Parameters and Depth of backbone model used in this paper. This table summarizes the properties of the backbone models. The size column illustrates how many space need to store the model in megabyte. The parameters column demonstrate the number of parameters in the associated model. The last column, depth show the number of hidden layers in that model. Parameters and Depth are two crucial element to evaluate the optimized model stated in the Objective section.}
	\label{table:model-summary}
\end{table}

@@

In this paper, the Soft-Attention layer is applied in the same way in this paper \cite{03358}. The Soft-Attention module is described in the following diagram:

@@

\subsubsection{Tools}
TensorFlow and Keras are two of the most popular framework to build deep learning model. In this research, Keras based on TensorFlow is used to build, clone the backbone model which is pre-trained with the image-net data set. Otherwise, the models are trained by NVIDIA RTX TitanV and the data set is pre-processed with the CPU Intel I5 32 processors, RAM 32GB. In detail, the GPU is setup with CUDA 11.6, cuDNN 8.3 and ChipSRT as the requirement of TensorFlow version 2.7.0.
\subsubsection{Evaluation Metrics}
\begin{figure}[!htb]
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=1.1\linewidth]{Definitions/Confusion-matrix}
		\caption{Confusion Matrix}\label{fig:confusion-matrix}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=.7\linewidth]{Definitions/AUC}
		\caption{Area Under the Curve}\label{fig:AUC}
	\end{minipage}
\end{figure}
The model is evaluated by using the confusion matrix and related metrics. The figure 4 illustrates the presentation of a $2 \times 2$ confusion matrix used for $2$ class. Consider a confusion matrix $A$ with $C$ number of class. Let $A^i$ and $A^j$ is the set of $A$ rows and columns respectively, therefore $A^i_k$ is the element at row i and column k
\[
A = \begin{bmatrix}
	a_{11} & a_{12} & \dots & a_{1j} \\
	a_{21} & a_{22} & \dots & a_{2j} \\
	\vdots & \vdots	&  & \vdots\\
	a_{i1} & a_{i2} & \dots & a_{ij} 
\end{bmatrix}
\]
The True Positive(TP) of all class in this case is the main diagonal of the matrix $A$. The following method are used to calculate the False Positives(FP), False Negatives(FN), and True Negatives(TN) of all class:
\[
FP = -TP + \sum_{k=1}^{i}A^i_k \hspace{1cm} FN = -TP + \sum_{k=1}^{j}A^j_k
\]
\[
TN_c = \sum_{i=1}^{C}\sum_{j=1}^{C}a_{ij} - \left[ \sum_{k=1}^{i}A^i_{i=c k} + \sum_{k=1}^{j}A^j_{j=c k} \right] + a_{i=c j=c} \implies TN = \begin{bmatrix}
	TN_1 & TN_2 & \dots & TN_c
\end{bmatrix}
\]
Then, the model is evaluated by the following metrics:
\[\text{Sensitivity(Sens)} = \frac{TP}{TP + FN} \hspace{1cm} \text{Specificity(Spec)} = \frac{TN}{TN + FP}\]
where Sensitivity and specificity mathematically describe the accuracy of a test which reports the presence or absence of a condition. Individuals for which the condition is satisfied are considered "positive" and those for which it is not are considered "negative". Sensitivity or true positive rate refers to the probability of a positive test, conditioned on truly being positive while Specificity  or true negative rate refers to the probability of a negative test, conditioned on truly being negative.
\[\text{Precision} = \frac{TP}{TP + FP} \hspace{1cm} \text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\]
Precision or positive predictive value (PPV) is the probability of a positive test conditioned on both truly being positive or negative. F1-score, on the other hand refers the harmonic mean of precision and recall which mean the higher the f1-score is, the higher both precision and recall is. Besides, the expected value of precision, f1-score and recall-score are also applied because of the multi-class problem.
\[\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN} \hspace{1cm} \text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}\]
The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve (ROC) that indicate the probability of TP versus the probability of FP.

@@

According to the Figure 10, it is clear that the model trained with metadata has a higher accuracy than the model trained with augmented data only. While InceptionResNetV2 and DenseNet201 trained with augmented data have accuracy of $0.79$ and $0.84$ respectively, their training with metadata are $0.90$ and $0.89$, respectively. Furthermore, Resnet50 trained with metadata data has the accuracy that outperform the Resnet50 trained with augmented data and is twice as high as Resnet152 trained with metadata. On the other hand, mobile model including MobileNetV2, MobileNetV3Large, and NasNetMobile, even though has a much smaller number of parameters and depth than the other model, they have a quite good accuracy of $0.81$, $0.86$, $0.86$, respectively.

Moreover, the model trained with augmented data does not only have low accuracy but their f1-score and the recall score also are imbalanced according to figure 10, 11, 12, 13. As a results, augmented data model does not classify well on all class as InceptionResNetV2 trained on augmented data have f1-score on class df and akiec is just above $0.3$ and $0.4$, separately while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way arcoding to the figure 12. However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class. The others still face the imbalanced term. Since this data set is not balanced, therefore using augmented data can make the model more  bias to the class which has larger sample. Using the metadata, though still make the model bias, it does contributes to the improvement of  the performance of the model.

@@

This problem is also true with the recall score according to fugure 13. DenseNet201, InceptionResNetV2, trained with augmented data has expected value of recall of $0.56$, $0.69$, respectively, while the combination of DenseNet201, Metadata and the new weight loss function achieve the expected value of recall: $0.82$. Therefore, metadata does improve the model performance by reducing the amount of data needed for achieving higher results. On the other hand, the reason why the model become much more balanced is the weighted loss function. Weight loss function has ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class. DenseNet201, InceptionResNetV2 trained with the new weighted loss function have recall in akiec of $0.85$. $0.82$, respectively, as opposed to their training in akiec without weighted loss function: $0.65$ and $0.37$.

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/den re}
	\caption{The comparison between recal scores of DenseNet201 trained with augmented data and the one trained with metadata and weight loss}
	\label{fig:den recall}
\end{figure}
\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/in re}
	\caption{The comparison between recall scores of InceptionResNetV2 trained with augmented data and the one trained with metadata and weight loss}
	\label{fig:incep recall}
\end{figure}

Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance. MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately according to the  table A4 appendix C.2.  It's transparent that MobileNetV3Large and NasNetMobile are the two best performance model. Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile.

@@

The table 5 shows that the MobileNetV3Large, though the number of parameters are much smaller than the DenseNet201, InceptionResNetV2, achieve the accuracy nearly to the others. In detail, MobileNetV3Large whose the number of parameters is 5.5 millions which is four and ten times less than DenseNet201 and InceptionResNetV2, respectively. The depth of MobileNetV3Large, on the other hand, is four times less than DenseNet201, InceptionResNetV2 which are 118 hidden layers as opposed to 402, 449 of DenseNet201 and InceptionResNetV2, separately. Although, the MobileNetV3Larege only achieve the accuracy of 0.86 the time need for prediction is 10 and 30 times less than the other opponents. If the MobileNetV3Large need a harder process of parameter hyper-tuning to achieve a better result, which is also the future target of this research.

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/ADvsMD}
	\caption{ROC AUC Score. This figure illustrate the AUC score associated with models including models trained with augmented data and models trained with metadata}
	\label{fig:ADvsDC-AUC}
\end{figure}

The figure 15 shows the AUC score of the three models InceptionResNetV2, Densenet201, and ResNet50 which is trained with only augmented data or metadata. It's transparent that the InceptionResNetV2 and DenseNet201 have higher AUC-score trained with metadata: 0.974 and 0.971 as opposed to 0.972 and 0.93, respectively. ResNet50 trained with augmented data, on the other hand have higher auc-score: 0.95 as compared to 0.93 of ResNet50 trained with metadata. Overall, InceptionResNetV2 trained with metadata reach the peak with the auc-score of 0.974. The InceptionResNetV2 trained with metadata is also compared with the others to find out the best models trained. According to the figure 15, the InceptionResNetV2 still hit the peak of 0.974 auc-score. ResNet152, otherwise is the worst model with the auc-score of 0.87. Other models, on the other hand have the approximately same of auc-score.

>>>>

\address{
$^{1}$ \quad School of Electrical and Electronic Engineering, Hanoi university of Science and Technology, Vietnam\\
$^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, Vietnam\\
$^{3}$ \quad School of Electrical and Electronic Engineering, Hanoi university of Science and Technology, Vietnam}

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Today, the rapid development of industrial zones leads to an increased incidence of skin	diseases because of polluted air. According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffering from skin cancer and more than 7600 of these people will not survive. In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential. Along with the strong development of artificial intelligence technologies, many solutions to support the diagnosis of skin diseases have been researched and developed. In this paper, a combination of SOTA model such as DenseNet, InceptionNet, ResNet, NasNet, and MobileNet and Soft-Attention is proposed. Furthermore, personal information including age and gender are also used. It is worth to note that a new loss function	that takes into account the data imbalance is also proposed. Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.989, respectively. Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of hidden layers is 4 times less, it achieves 0.86 accuracy and 30 times faster diagnosis than DenseNet201.
}

@@

\begin{table}
	\centering
	\begin{tabular}{| c | p{1.5cm} | p{1.5cm} | p{2cm} | p{1.5cm} | p{2cm} |}
		\hline
		Research & Deep Learning & Machine Learning & Data 
		Augmentation & Feture Extraction & Data set\\
		\hline
		\cite{03358} & x & & x & & HAM10000\\
		\hline
		\cite{03798} & x & x & x & x & HAM10000\\
		\hline
		\cite{10348} & x & x & x & & HAM10000, $PH^2$\\
		\hline
		\cite{09418} & x & & x & & HAM10000\\
		\hline
		\cite{01284} & x & & x & & HAM10000\\
		\hline
		\cite{06612} & x & & x & x & HAM10000, BCN-20000, MSK\\
		\hline
		\cite{03225} & x & & x & & HAM10000\\
		\hline
		\cite{12602} & x & & x & & HAM10000\\
		\hline
		\cite{03426} & x & & x & & HAM10000\\
		\hline
		\cite{03910} & x & & x & & HAM10000\\
		\hline
		\cite{05045} & & x & x & x & HAM10000\\
		\hline
	\end{tabular}
	\caption{Related Works Summary.}
	\label{table:related-work-summary}
\end{table}
\subsection{Proposed Method}
In this research, a new model is constructed from the combination of:\\
- Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and MobileNetV2/V3\\
- Using metadata including age, gender, localization as another input of the model\\
- Using Soft-Attention as a feature extractor of the model\\
- A new weight loss function
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
\subsection{Materials}
\subsubsection{Image Data}
The data set used in this paper is the HAM10000 data set published by Havard University Dataverse \cite{10417}. There are total 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the data set is shown in the Table \ref{table:data-distribution} below:

\begin{table}[H]
	\centering
	\begin{tabular}{|c c c c c c c c c|} 
		\hline
		Class & AKIEC & BCC & BKL & DF & MEL & NV & VASC & Total \\ 
		\hline
		No. Sample & 327 & 514 & 1099 & 115 & 1113 & 6705 & 142 & 10015 \\
		\hline
	\end{tabular}
	\caption{Data Distribution in HAM10000.}
	\label{table:data-distribution}
\end{table}

@@

\subsubsection{Metadata}
The HAM10000 data set \cite{10417} also contain the metadata of patient including gender, age, and the capturing position illustrated in Table \ref{table:metadata sample}
\begin{table}[H]
	\centering
	\begin{tabular}{|c c c c |} 
		\hline
		ID & Age & Gender & Local\\ 
		\hline
		ISIC-00001 & 15 & Male & back\\
		\hline
		ISIC-00002 & 85 & Female & elbow\\
		\hline
	\end{tabular}
	\caption{Metadata example in the data set}
	\label{table:metadata sample}
\end{table}
\subsection{Methodology}
\subsubsection{Overall Architecture}
The whole architecture of the model is represented in the Figure \ref{fig:main-model}. The model takes two input including Image data and Metadata. Metadata branch, otherwise is preprocessed before feeding into a dense layer then concatenate with the output of Soft-Attention layer.

@@

The Figure \ref{fig:model-structure} illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research. In detailed the combination of DenseNet201 and Soft-Attention is formed by replacing the three last DenseBlock, Global Average Pooling, and the fully-connected layer with the Soft-Attention Module. Similarity, ResNet50 and ResNet152 is also replaced the three last Residual Block, Global Average Pooling, and the fully connected layer with the Soft-Attention module. InceptionResNetV2, on the other hand, is replaced the Average Pool and the last Dropout with the Soft-Attention Module. Besides, the two last Normal Cell in NasNetLarge is replaced with the Soft-Attention module.

@@

The Figure \ref{fig:mobile-model-structure}, on the other hand shows the detailed structure of mobile-based mobile and its combination with Soft-Attention. All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution 1x1 by Soft-Attention module. The NasNetMobile, otherwise, combine with the Soft-Attention module by replacing the last Normal Cell. 
\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/Mobile Model Structure}
	\caption{Overall Mobile-based Model Architecture. This figure show the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile. The detail structure and information can be found at the Apendix \ref{appendix-table:detailed mobile model structure}}
	\label{fig:mobile-model-structure}
\end{figure}

@@

In this research, the unknowns is kept as a type as discussed in Metadata section. Sex, anatomical site and age are also category encoded and numerical normalized, respectively. After processing, the metadata is then concatenated and fed into a dense layer of 4096 neurons. Finally, this this dense layer is then concatenate with the output of Soft-Attention which is then discussed in Soft-Attention section. The Input schema is described in the Table \ref{fig:input-schema}

@@

\begin{table}[H]
	\centering
	\begin{tabular}{|l | c c c|} 
		\hline
		Model & Size(MB) & Parameters & Depth \\ 
		\hline
		Resnet50 & 98 & 25.6M & 107 \\ 
		\hline
		Resnet152 & 232 & 60.4M & 311 \\ 
		\hline
		DenseNet201 & 80 & 20.2M & 402 \\
		\hline
		InceptionResNetV2 & 215 & 55.9M & 449 \\
		\hline
		MobileNet & 16 & 4.3M & 55 \\ 
		\hline
		MobileNetV2 & 14 & 3.5M & 105 \\ 
		\hline
		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
		\hline
		MobileNetV3Large & Unknown & 5.5M & 118 \\
		\hline
		NasnetMobile & 23 & 5.3M & 308 \\
		\hline
		NasnetLarge & 343 & 88.9M & 533 \\ 
		\hline
	\end{tabular}
	\caption{Size and Parameters and Depth of backbone model used in this paper.}
	\label{table:model-summary}
\end{table}

@@

In this research, the Soft-Attention layer is applied in the same way in this research \cite{03358}. The Soft-Attention module is described in the figure \ref{fig:soft-attention-block}

@@

\subsubsection{Tools}
TensorFlow and Keras are two of the most popular framework to build deep learning model. In this research, Keras based on TensorFlow is used to build, clone the backbone model which is pre-trained with the image-net data set. Otherwise, the models are trained by NVIDIA RTX TitanV and the data set is pre-processed with the CPU Intel I5 32 processors, RAM 32GB. In detail, the GPU is setup with CUDA 11.6, cuDNN 8.3 and ChipSRT as the requirement of TensorFlow version 2.7.0.
\subsubsection{Evaluation Metrics}
\begin{figure}[!htb]
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=1.1\linewidth]{Definitions/Confusion-matrix}
		\caption{Confusion Matrix}\label{fig:confusion-matrix}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=.7\linewidth]{Definitions/AUC}
		\caption{Area Under the Curve}\label{fig:AUC}
	\end{minipage}
\end{figure}
The model is evaluated by using the confusion matrix and related metrics. The Figure \ref{fig:confusion-matrix} illustrates the presentation of a $2 \times 2$ confusion matrix used for $2$ class. Consider a confusion matrix $A$ with $C$ number of class. Let $A^i$ and $A^j$ is the set of $A$ rows and columns respectively, therefore $A^i_k$ is the element at row i and column k
\[
A = \begin{bmatrix}
	a_{11} & a_{12} & \dots & a_{1j} \\
	a_{21} & a_{22} & \dots & a_{2j} \\
	\vdots & \vdots	&  & \vdots\\
	a_{i1} & a_{i2} & \dots & a_{ij} 
\end{bmatrix}
\]
The True Positive(TP) of all class in this case is the main diagonal of the matrix $A$. The following method are used to calculate the False Positives(FP), False Negatives(FN), and True Negatives(TN) of all class:
\[
FP = -TP + \sum_{k=1}^{i}A^i_k \hspace{1cm} FN = -TP + \sum_{k=1}^{j}A^j_k
\]
\[
TN_c = \sum_{i=1}^{C}\sum_{j=1}^{C}a_{ij} - \left[ \sum_{k=1}^{i}A^i_{i=c k} + \sum_{k=1}^{j}A^j_{j=c k} \right] + a_{i=c j=c} \implies TN = \begin{bmatrix}
	TN_1 & TN_2 & \dots & TN_c
\end{bmatrix}
\]
Then, the model is evaluated by the following metrics:
\[\text{Sensitivity(Sens)} = \frac{TP}{TP + FN} \hspace{1cm} \text{Specificity(Spec)} = \frac{TN}{TN + FP}\]
where Sensitivity and specificity mathematically describe the accuracy of a test which reports the presence or absence of a condition. Individuals for which the condition is satisfied are considered "positive" and those for which it is not are considered "negative". Sensitivity or true positive rate refers to the probability of a positive test, conditioned on truly being positive while Specificity  or true negative rate refers to the probability of a negative test, conditioned on truly being negative.
\[\text{Precision} = \frac{TP}{TP + FP} \hspace{1cm} \text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\]
Precision or positive predictive value (PPV) is the probability of a positive test conditioned on both truly being positive or negative. F1-score, on the other hand refers the harmonic mean of precision and recall which mean the higher the f1-score is, the higher both precision and recall is. Besides, the expected value of precision, f1-score and recall-score are also applied because of the multi-class problem.
\[\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN} \hspace{1cm} \text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}\]
The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve (ROC) that indicate the probability of TP versus the probability of FP.

@@

According to the Table \ref{table:overall-acc}, it is clear that the model trained with metadata has a higher accuracy than the model trained with augmented data only. While InceptionResNetV2 and DenseNet201 trained with augmented data have accuracy of $0.79$ and $0.84$ respectively, their training with metadata are $0.90$ and $0.89$, respectively. Furthermore, Resnet50 trained with metadata data has the accuracy that outperform the Resnet50 trained with augmented data and is twice as high as Resnet152 trained with metadata. On the other hand, mobile model including MobileNetV2, MobileNetV3Large, and NasNetMobile, even though has a much smaller number of parameters and depth than the other model, they have a quite good accuracy of $0.81$, $0.86$, $0.86$, respectively.

\begin{table}[H]
	\centering
	\begin{tabular}{| l | c  c | }
		\hline
		Model & ACC(AD) & ACC(MD)\\ 
		\hline
		InceptionResNetV2 & 0.79 & \textbf{0.90}\\
		\hline
		DenseNet201 & 0.84 & \textbf{0.89}\\
		\hline
		ResNet50 & 0.76 & 0.70 \\
		\hline
		ResNet152 & - & 0.57\\
		\hline
		NasNetLarge & - & 0.84\\
		\hline
		MobileNetV2 & - & 0.81\\
		\hline
		MobileNetV3Small & - & 0.78\\
		\hline
		MobileNetV3Large & - & \textbf{0.86}\\
		\hline
		NasNetMobile & - & \textbf{0.86}\\
		\hline
	\end{tabular}
	\caption{Accuracy of all models. ACC stands for accuracy. AD stands for augmented data, this indicate that the model is trained with augmented data. MD stands for Metadata which indicate that the model is trained with Metadata}
	\label{table:overall-acc}
\end{table}

Moreover, the model trained with augmented data does not only have low accuracy but their f1-score and the recall score also are imbalanced according to Figure \ref{fig:den f1}, \ref{fig:incep f1}, \ref{fig:den recall}, and \ref{fig:incep recall}. As a results, augmented data model does not classify well on all class as InceptionResNetV2 trained on augmented data have f1-score on class df and akiec is just above $0.3$ and $0.4$, separately while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way arcoding to the Figure \ref{fig:incep f1}. However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class. The others still face the imbalanced term. Since this data set is not balanced, therefore using augmented data can make the model more  bias to the class which has larger sample. Using the metadata, though still make the model bias, it does contributes to the improvement of  the performance of the model.

@@

This problem is also true with the recall score according to Figure \ref{fig:den recall} and \ref{fig:incep recall}. DenseNet201, InceptionResNetV2, trained with augmented data has expected value of recall of $0.56$, $0.69$, respectively, while the combination of DenseNet201, Metadata and the new weight loss function achieve the expected value of recall: $0.82$. Therefore, metadata does improve the model performance by reducing the amount of data needed for achieving higher results. On the other hand, the reason why the model become much more balanced is the weighted loss function. Weight loss function has ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class. DenseNet201, InceptionResNetV2 trained with the new weighted loss function have recall in akiec of $0.85$. $0.82$, respectively, as opposed to their training in akiec without weighted loss function: $0.65$ and $0.37$.

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/den re}
	\caption{The comparison between recal scores of DenseNet201 trained with augmented data and the one trained with metadata and weight loss}
	\label{fig:den recall}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/in re}
	\caption{The comparison between recall scores of InceptionResNetV2 trained with augmented data and the one trained with metadata and weight loss}
	\label{fig:incep recall}
\end{figure}

Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance. MobileV3large, MobileV3Small, NasNetLarge and NasNetMobile outperform others on classifying class df with the recall score of $0.92$, $1$, $0.92$, $0.92$, separately according to the Table \ref{appendix-table:mobile-performance}. It's transparent that MobileNetV3Large and NasNetMobile are the two best performance model. Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile.

@@

The Table \ref{table:optimized-performance-mobile-model} shows that the MobileNetV3Large, though the number of parameters are much smaller than the DenseNet201, InceptionResNetV2, achieve the accuracy nearly to the others. In detail, MobileNetV3Large whose the number of parameters is 5.5 millions which is four and ten times less than DenseNet201 and InceptionResNetV2, respectively. The depth of MobileNetV3Large, on the other hand, is four times less than DenseNet201, InceptionResNetV2 which are 118 hidden layers as opposed to 402, 449 of DenseNet201 and InceptionResNetV2, separately. Although, the MobileNetV3Larege only achieve the accuracy of 0.86 the time need for prediction is 10 and 30 times less than the other opponents. If the MobileNetV3Large need a harder process of parameter hyper-tuning to achieve a better result, which is also the future target of this research.

The Table \ref{table:overall-auc} shows the AUC score of the three models InceptionResNetV2, Densenet201, and ResNet50 which is trained with only augmented data or metadata. It's transparent that the InceptionResNetV2 and DenseNet201 have higher AUC-score trained with metadata: 0.974 and 0.971 as opposed to 0.972 and 0.93, respectively. ResNet50 trained with augmented data, on the other hand have higher auc-score: 0.95 as compared to 0.93 of ResNet50 trained with metadata. Overall, InceptionResNetV2 trained with metadata reach the peak with the auc-score of 0.974. The InceptionResNetV2 trained with metadata is also compared with the others to find out the best models trained. According to the figure 15, the InceptionResNetV2 still hit the peak of 0.974 auc-score. ResNet152, otherwise is the worst model with the auc-score of 0.87. Other models, on the other hand have the approximately same of auc-score.
